<<<<<<< HEAD
---
title: "Shiny_fire"
author: "Kyle Monper"
date: "January 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(tidyverse)
library(sf)
library(leaflet)
library(shiny)
library(plotly)
library(spData)
library(varhandle)
library(RColorBrewer)
library(colorspace)
require(sp)
require(rgdal)
require(maps)
```

```{r}
# Read in the data

fire <- st_read("Fire_Output.shp")

eco <- st_read("ca_eco.shp") %>% 
  dplyr::select(US_L3NAME) %>% 
  rename(Region = US_L3NAME) %>% 
  st_simplify(dTolerance = 100) %>% # Simplify polygons so maps don't take forever to load
  st_transform(crs = 4326)
```


```{r}

top100 <- fire %>% 
  select(YEAR_, FIRE_NAME,GIS_ACRES, CAUSE) %>% 
  arrange(-GIS_ACRES)

top100$YEAR_ <- unfactor(top100$YEAR_)

top100 <- top100[1:100,] %>% 
  mutate(CAUSE = case_when(
    CAUSE == 1 ~ "Lightning",
    CAUSE == 2 ~ "Equipment Use",
    CAUSE == 4 ~ "Campfire",
    CAUSE == 5 ~ "Debris",
    CAUSE == 6 ~ "Railroad",
    CAUSE == 7 ~ "Arson",
    CAUSE == 9 ~ "Miscellaneous",
    CAUSE == 10 ~ "Vehicle",
    CAUSE == 11 ~ "Power Line",
    CAUSE == 14 ~ "Unknown/Unidentified"
  )) %>% 
  arrange(YEAR_)


```

try this for simplifying the polygons
```{r}
top100 <- top100 %>% 
  st_simplify(dTolerance = 5000)
```

```{r}
#Testing to see if wrangling done in Shiny actually does what its supposed to
reactive_cause_test <- top100 %>%
      filter(CAUSE == "Miscellaneous") %>% 
      group_by(YEAR_) %>% 
      summarize(acres_burn_tot = sum(GIS_ACRES))
```

```{r}
top100 <- st_transform(top100, crs = 4326)

centroid <- st_centroid(top100)


centroid_less <- centroid %>% 
  mutate(lat = unlist(map(centroid$geometry,1)),
           long = unlist(map(centroid$geometry,2))) %>% 
  select(GIS_ACRES, lat, long) %>% 
  st_drop_geometry()


top100 <- merge(top100, centroid_less, by = "GIS_ACRES")
```

```{r}

top100 <- fire %>% 
  select(YEAR_, FIRE_NAME,GIS_ACRES, CAUSE) %>% 
  arrange(-GIS_ACRES)

top100$YEAR_ <- unfactor(top100$YEAR_)

top100 <- top100[1:100,] %>% 
  mutate(CAUSE = case_when(
    CAUSE == 1 ~ "Lightning",
    CAUSE == 2 ~ "Equipment Use",
    CAUSE == 4 ~ "Campfire",
    CAUSE == 5 ~ "Debris",
    CAUSE == 6 ~ "Railroad",
    CAUSE == 7 ~ "Arson",
    CAUSE == 9 ~ "Miscellaneous",
    CAUSE == 10 ~ "Vehicle",
    CAUSE == 11 ~ "Power Line",
    CAUSE == 14 ~ "Unknown/Unidentified"
  )) %>% 
  arrange(YEAR_)
```

try this for simplifying the polygons
```{r}
top100 <- top100 %>% 
  st_simplify(dTolerance = 5000)
```

```{r}
#Testing to see if wrangling done in Shiny actually does what its supposed to
reactive_cause_test<- top100 %>%
      filter(CAUSE == "Miscellaneous") %>% 
      group_by(YEAR_) %>% 
      summarize(acres_burn_tot = sum(GIS_ACRES))
```

```{r}
top100 <- st_transform(top100, crs = 4326)

centroid <- st_centroid(top100)


centroid_less <- centroid %>% 
  mutate(lat = unlist(map(centroid$geometry,1)),
           long = unlist(map(centroid$geometry,2))) %>% 
  select(GIS_ACRES, lat, long) %>% 
  st_drop_geometry()


top100 <- merge(top100, centroid_less, by = "GIS_ACRES")

```

```{r}

# Eco region wrangling and pie-chart
eco_intersect <- eco %>% 
  st_intersection(top100)

eco_pie_df <- st_set_geometry(eco_intersect, NULL)

eco_pie <- data.frame(eco_pie_df)
  
#eco_pie2 <- eco_pie[, c('Region', 'GIS_ACRES')]

#mapcolours <- data.frame(x = c("Cascades","Central Basin and Range","Central California Foothills and Coastal Mountains","Central California Valley", "Eastern Cascades Slopes and Foothills","Klamath Mountains/California High North Coast Range","Mojave Basin and Range","Northern Basin and Range","Sierra Nevada","Sonoran Basin and Range","Southern California Mountains","Southern California Mountains","Southern California/Northern Baja Coast"),
 #                       colours = c('rgb(70,130,180)', 'rgb(46,139,87)', 'rgb(128,128,0)', 'rgb(0,128,128)', 'rgb(222,184,135)','rgb(188,143,143)', 'rgb(184,134,11)', 'rgb(160,82,45)', 'rgb(105,105,105)', 'rgb(47,79,79)','rgb(112,128,144)','rgb(112,128,144)','rgb(112,128,144)'),
  #                      stringsAsFactors = FALSE)


colors <- c('rgb(70,130,180)', 'rgb(46,139,87)', 'rgb(128,128,0)', 'rgb(0,128,128)', 'rgb(222,184,135)','rgb(188,143,143)', 'rgb(184,134,11)', 'rgb(160,82,45)', 'rgb(105,105,105)', 'rgb(47,79,79)','rgb(112,128,144)','rgb(112,128,144)','rgb(112,128,144)')

pie <- plot_ly(eco_pie, labels = ~Region, values = ~GIS_ACRES, type = 'pie', marker = list(color = colors)) %>% 
               layout(title = 'Acres Burned',
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

pie

# Trying pie chart with ggplot - may be easier to customize colors this way

eco_pie2 <- eco_pie %>% 
  group_by(Region, YEAR_) %>% 
  mutate(volume = sum(GIS_ACRES)) %>% 
  mutate(share = volume/sum(volume)*100)


ggpie <- ggplot(eco_pie2, aes(x = "", y = GIS_ACRES, fill = Region)) +
  geom_bar(width = 1, stat = "identity") +
  geom_text(aes(label = paste0(round(share), "%")),
            position = position_stack(vjust = 0.5)) +
  labs(x = NULL, y = NULL, fill = NULL) +
  scale_fill_manual(values = c("yellow4", "wheat4", "tomato3", "olivedrab", "steelblue4", "indianred3", "sienna3", "rosybrown4", "orange4", "lightgoldenrod4", "goldenrod4", "cadetblue4")) +
  theme_classic() +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())

```

```{r}
#Experiementing with Fire Causes plot:

#  ggplot(data = reactive_cause(), aes(x = YEAR_, y = acres_burn_tot_1000))+
 #     geom_col(fill = "firebrick1", colour = "firebrick4", width = 5, position = "stack")+
  #    theme_classic()+
   #   scale_x_continuous(expand = c(0,0), limit = c(1877,2018))+
    #  scale_y_continuous(expand = c(0,0), limit = c(0, 510))+
     # labs(y = "Fire Size (Thousands of Acres)", x = "Year")

```
